Automated Topic Naming

### 2012-03-16 ese/ese.tex
author reference

We wanted to see whether developers in the PostgreSQL project\footnote{Since the MySQL and MaxDB data had poor records for developer ids, we focused on PostgreSQL.} worked on similar NFRs. For example, one developer might be a usability expert, while
another developer is focused on security. We assume that the NFR labels associated with a commit implicitly reflect work on those NFRs. Being able to report on where effort is being expended is useful for tracking productivity (among other things).
%Within this section we focused on PostgreSQL.
We explored this issue by extracting, for each topic in the PostgreSQL data-set, the developer names responsible for the commits used to generate that topic, and 
the NFRs that are associated with the topic. 
The analysis in this section used Neil's annotations.
This produced a map which associated developer name with NFR
labels. The six NFR labels (\emph{maintainability, usability,
  efficiency, functionality, portability, reliability}) and the
\emph{None} label describe a 7-dimensional space (essentially a distribution), into which we can position developers, based on the frequency with which each label occurs in the map.

@@

\subsection{Inter-rater reliability}
\label{sec:inter-rater}
To determine inter-rater reliability two of the authors---Ernst and Hindle---each annotated the PostgreSQL topics,
and then evaluated each other's annotations. 
Table \ref{tab:interr} describes the Cohen Kappa and the Spearman
correlation of our per-topic annotations for each NFR. We 
evaluated inter-rater reliability using each NFR, because a single topic could be
tagged with more than one NFR.

@@

To evaluate our results empirically, we compared them to the annotations that would result if the seven labels
 were applied randomly. In the first simulation, as shown by Figure \ref{fig:irr},
we sampled with replacement from our own NFR label distributions to
produce random ratings that looked like our own. We then applied the
Kappa-statistic on this sampling and our labelling, and repeated
this 100,000 times. We then compared this distribution of simulated
IRR ratings against our own IRR ratings. We found that
for 4 out of 7 NFR labels, the IRR values for our labels were greater than the random
IRR measures 96\% of the time. For \emph{portability} and \emph{efficiency}, our IRR
was greater 100\% of the time both for Neil's ratings, Abram's ratings
and the union of both Neil and Abram. 
We know this by evaluating our IRR ratings against the empirical
cumulative distribution function (ECDF) of the IRR ratings of the 100,000
simulation runs.
One explanation of the positive result for \emph{portability} is that such changes are often 
accompanied by clear indicator terms such as \emph{Windows, Linux, SunOS}, etc.

@@

Were our results harmed by low IRR scores? For MaxDB and MySQL, since
each annotator (Neil or Abram) acted as the sole oracle, the results
for either system still stand, but construct validity is harmed since 
it is not clear if the annotated NFR actually represented the NFR relevant to that commit.
 The measured empirical performance of each system still
stands, but the comparison between systems in terms of NFRs might be
harmed by low IRR scores.

>>>>

We wanted to see whether developers in the PostgreSQL project\footnote{Since the MySQL and MaxDB data had poor records for developer ids, we focused on PostgreSQL.} worked on similar NFRs. For example, one developer might be a usability expert, while
another developer is focused on security. We assume that the NFR labels associated with a commit implicitly reflect work on those NFRs. Being able to report on where effort is being expended is useful for tracking productivity (among other things).
%Within this section we focused on PostgreSQL.
We explored this issue by extracting, for each topic in the PostgreSQL data-set, the developer names responsible for the commits used to generate that topic, and 
the NFRs that are associated with the topic. 
The analysis in this section used author 2's annotations.
This produced a map which associated developer name with NFR
labels. The six NFR labels (\emph{maintainability, usability,
  efficiency, functionality, portability, reliability}) and the
\emph{None} label describe a 7-dimensional space (essentially a distribution), into which we can position developers, based on the frequency with which each label occurs in the map.

@@

\subsection{Inter-rater reliability}
\label{sec:inter-rater}
To determine inter-rater reliability two of the authors---author 1 and author 2---each annotated the PostgreSQL topics,
and then evaluated each other's annotations. 
Table \ref{tab:interr} describes the Cohen Kappa and the Spearman
correlation of our per-topic annotations for each NFR. We 
evaluated inter-rater reliability using each NFR, because a single topic could be
tagged with more than one NFR.

@@

To evaluate our results empirically, we compared them to the annotations that would result if the seven labels
 were applied randomly. In the first simulation, as shown by Figure \ref{fig:irr},
we sampled with replacement from our own NFR label distributions to
produce random ratings that looked like our own. We then applied the
Kappa-statistic on this sampling and our labelling, and repeated
this 100,000 times. We then compared this distribution of simulated
IRR ratings against our own IRR ratings. We found that
for 4 out of 7 NFR labels, the IRR values for our labels were greater than the random
IRR measures 96\% of the time. For \emph{portability} and \emph{efficiency}, our IRR
was greater 100\% of the time both for author 2's ratings, author 1's ratings
and the union of both authors 1 and 2. 
We know this by evaluating our IRR ratings against the empirical
cumulative distribution function (ECDF) of the IRR ratings of the 100,000
simulation runs.
One explanation of the positive result for \emph{portability} is that such changes are often 
accompanied by clear indicator terms such as \emph{Windows, Linux, SunOS}, etc.

@@

Were our results harmed by low IRR scores? For MaxDB and MySQL, since
each annotator (author 2 or author 1) acted as the sole oracle, the results
for either system still stand, but construct validity is harmed since 
it is not clear if the annotated NFR actually represented the NFR relevant to that commit.
 The measured empirical performance of each system still
stands, but the comparison between systems in terms of NFRs might be
harmed by low IRR scores.
